### 2019-05-21 reviews/response.md

We thank the reviewers for their detailed and insightful feedback.

We have added three new implementations to Task Bench: Dask,
MPI+OpenMP and MPI+CUDA. Results are included in the evaluation
section.

One of the salient features of Task Bench is that it permits the
implementation of a benchmark with M configurations and N systems with
an amount of effort that is O(M+N) rather than O(MN). We have updated
the introduction to reflect this.

In response to specific reviewer questions:

### 2019-05-22 1_introduction.tex
Only claim 15 systems so we don't have to quibble about MPI+CUDA not running on Cori.

We conduct a comprehensive comparative study of Task Bench
implementations in 13 different programming systems:
Chapel \cite{Chapel15}, Charm++ \cite{Charmpp93}, MPI \cite{MPI},
OmpSs \cite{OmpSs11}, OpenMP \cite{OpenMPSpec40},
PaRSEC \cite{PARSEC13}, Realm \cite{Realm14}, Regent \cite{Regent15},
Spark \cite{Spark10}, StarPU \cite{StarPU11},
Swift/T \cite{Wozniak13}, TensorFlow \cite{TensorFlow15}, and
X10 \cite{X1005}. Using METG(50\%), we determine the baseline
runtime overhead of each system along with overheads associated with
increasing numbers of and/or variations in the pattern of dependencies. We
also explore each system's ability to scale, hide communication
overhead, and mitigate load imbalance.

@@

\begin{itemize}
\item Section~\ref{sec:metg} defines the METG(50\%) metric and its
  relationship to quantities of interest to application developers.
\item Section~\ref{sec:task-bench} describes the design of Task Bench.
\item Section~\ref{sec:implementation} details the implementation of
  Task Bench in 13 programming systems.
\item Section~\ref{sec:evaluation} provides a comprehensive evaluation
  of Task Bench on up to 256 Haswell nodes of the Cori
  supercomputer~\cite{Cori}.
\end{itemize}

>>>>

We conduct a comprehensive comparative study of Task Bench
implementations in 15 different programming systems:
Chapel \cite{Chapel15}, Charm++ \cite{Charmpp93}, Dask \cite{Dask}, MPI \cite{MPI}, MPI+X (OpenMP and CUDA),
OmpSs \cite{OmpSs11}, OpenMP \cite{OpenMPSpec40},
PaRSEC \cite{PARSEC13}, Realm \cite{Realm14}, Regent \cite{Regent15},
Spark \cite{Spark10}, StarPU \cite{StarPU11},
Swift/T \cite{Wozniak13}, TensorFlow \cite{TensorFlow15}, and
X10 \cite{X1005}. Using METG(50\%), we determine the baseline
runtime overhead of each system along with overheads associated with
increasing numbers of and/or variations in the pattern of dependencies. We
also explore each system's ability to scale, hide communication
overhead, and mitigate load imbalance.

@@

\begin{itemize}
\item Section~\ref{sec:metg} defines the METG(50\%) metric and its
  relationship to quantities of interest to application developers.
\item Section~\ref{sec:task-bench} describes the design of Task Bench.
\item Section~\ref{sec:implementation} details the implementation of
  Task Bench in 15 programming systems.
\item Section~\ref{sec:evaluation} provides a comprehensive evaluation
  of Task Bench on up to 256 Haswell nodes of the Cori
  supercomputer~\cite{Cori}.
\end{itemize}

### 2019-05-22 3_task_bench.tex
Add a code sample from Dask implementation.
Only claim 15 systems so we don't have to quibble about MPI+CUDA not running on Cori.

Despite its generality, Task Bench is easy to implement, making it
tractable to develop a suite of high-quality implementations. The central aspects of Task Bench, such as generating
task graphs and enumerating dependencies, are encapsulated in a core
library that is shared among all the Task Bench implementations. The
core library also includes implementations of the kernels, ensuring
that the kernels are identical in all systems, eliminating a potential
source of performance disparity that can be a pitfall for
implementations of mini-apps. Finally, the Task Bench core library manages the
parsing of input parameters and the display of output results,
ensuring that all implementations behave in a uniform manner and can
be scripted consistently. Because much of the functionality needed for
a Task Bench implementation is in the core library, implementations of
Task Bench are small: Our 16 Task Bench implementations range from 88
to 1500 lines, with several hundred lines being typical.

\input{f5_task_graphs}
\input{t0_equations}

>>>>

Despite its generality, Task Bench is easy to implement, making it
tractable to develop a suite of high-quality implementations. The central aspects of Task Bench, such as generating
task graphs and enumerating dependencies, are encapsulated in a core
library that is shared among all the Task Bench implementations. The
core library also includes implementations of the kernels, ensuring
that the kernels are identical in all systems, eliminating a potential
source of performance disparity that can be a pitfall for
implementations of mini-apps. Finally, the Task Bench core library manages the
parsing of input parameters and the display of output results,
ensuring that all implementations behave in a uniform manner and can
be scripted consistently. Because much of the functionality needed for
a Task Bench implementation is in the core library, implementations of
Task Bench are small: Our 15 Task Bench implementations range from 88
to 1500 lines, with several hundred lines being typical.

\input{f5_task_graphs}
\input{t0_equations}
\input{l1_code_sample}
